Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-09 main_paper.tex
Fix weak/strong inequality errors
The paper and literature use >= 0 for treatment and < 0 for control, but there
are a few instances in the paper where we mix up the weak and strong
inequalities. This commit fixes those errors.

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

>>>>

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.
